Rapid Georectification of Pushbroom Hyperspectral Imagery for Real Time Processing by an Autonomous Aerial Vehicle

### 2023-09-11 paper/paper.tex
Updates from Overleaf

\section{Introduction}
Overview of Hyperspectral Imagery

Multi-spectral vs Hyperspectral imagery

Paragraph about previous uses of HSI technology in remote sensing applications. Plant health, NDVI, water applications, land management, etc...

@@

Application: Our robotic team

The introduction should briefly place the study in a broad context and highlight why it is important. It should define the purpose of the work and its significance. The current state of the research field should be reviewed carefully and key publications cited. Please highlight controversial and diverging hypotheses when necessary. Finally, briefly mention the main aim of the work and highlight the principal conclusions. As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research. Citing a journal paper \cite{ref-journal}. Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}. Please use the command \citep{ref-thesis,ref-url} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences, Literature.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}
Overview of the HSI

Overview of the Aerial Vehicle Platform (w/ NUC and SSD)

@@

\subsection{Drone Components}

\subsection{Reflectance Conversion}

Here we can detail the conversion from radiance to reflectance using the downwelling irradiance spectrum with the assumption of a Lambertian surface.

\textbf{NOTE:} we should update the following three figures to make a single figure with the radiances/irradiance in on the left (using the left and right y-axis) and the reflectance on the right.

>>>>

\section{Introduction}

- Global change necessitating better sensing technology 
- Need to be able to track changes to water/plant/forest/land quality for better environmental management and disaster mitigation
    - Palestine Ohio
    - fires in Canada and Maui
    - Oil Spill clean up

- multi-spectral and hyper-spectral imaging
- in remote sensing
    - discuss satellite remote sensing 
    - multi-spectral platforms: MODIS, Sentinel, etc... 
    - upcoming hyper-spectral platforms:
- from Airplanes
- Land change tracking (water erosion, deforestation, desertification )
- Mention popular spectral indices like the NDVI

- Paragraph about use of drones for remote sensing 
    - smart agriculture
    - photogrametry and DEMs (Open Drone Map)

- Paragraph about the need of georectification 
    - Georectification = georeference + orthorectification
    - outline other papers that have discussed georectification techniques: 
        - ground control points 
        - IMU / GPS 
        - different type of sensors: square, pushbroom, whiskbroom

- Paragraph about difficulties of real time HSI application 
    - data volume (storage, transfer/streaming)
    - payload size 
    - what we really want (usually) isn't the full spectra at each pixel 
        - spectral indices (NDVI, etc.) 
        - Chemical concentrations (chlorophyll, crude oil, etc...)

- Paragraph about advances in hyper-spectral imaging technology, drones, and miniaturized computers (e.g. the raspberry pi, jetson nano, intel nuc, etc...)

- finally, introduce the paper via the Robot team --> e.g. cite the paper and talk about how we're going to focus on the drone in detail in this paper.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}

\subsection{Autonomous Aerial Vehicle}

subsection detailing the robot team, and specifically, the drone setup (HSI, NUC, Flir, etc...) 
- HSI takes images 
- IMU/GPS onboard position/orientation determination
- Intel NUC 1: manages HSI
- SSD
- Intel NUC 2: Processing 
- Ubiquity long-range wifi antenna (for streaming data products)

\subsection{Real time processing of HSI imagery}

- overview of processing pipeline

- Collection of raw HSI by imager
- Reading stored binary (ENVI) radiance data into tensor
- Reading Flight Data 
- Interpolate flight data from IMU to match HSI times
- Reading stored downwelling irradiance spectrum 
- Interpolate irradiance spectrum to match HSI $\lambda$s 
- Conversion to Reflectance under the assumption of a Lambertian surface (perfectly diffuse)
- Georectify to obtain new coordinates
- resample to regular grid
- compute derived $\lambda$-metrics (NDVI, etc...) 
- serve result (save to HDF5 or serve via web map service over wifi)

@@
